---
title: "Speed Of Straightening (from 6.5m to 2.5m)"
author: "Danlu"
date: "08/09/2019"
output: html_document
---

```{r Load the required libraries, echo=FALSE, message=FALSE, warning=FALSE}
library(multcomp); library(nlme); library(pastecs); library(data.table); 
```

To assess the difference in the speed of straightening of trajectories between conditions, we examined the change of target-heading angles as a function of distance.

# Change of target-heading angles of Trial 1 as a function of distance 
## Load the data
```{r}
load(file = '../../Data/segData.RData')
```

## Get the data ready
```{r}
starting_point_from_target <- 6.5
ending_point_from_target   <- 2.5

target_distance            <- 7

starting_point_for_walking <- target_distance - starting_point_from_target
ending_point_for_walking   <- target_distance - ending_point_from_target

segData_clean <- data.table(segData_clean)
offset_seg_trial1 <- segData_clean[Block %in% c(2, 4, 6, 8) & TrialNo == 1 & seg.z >= starting_point_for_walking & seg.z <= ending_point_for_walking]
offset_seg_trial1$Scene <- droplevels(offset_seg_trial1$Scene)
```

## Centralise the distance
```{r}
original_intercept <- as.numeric(unique(offset_seg_trial1$seg.z))[[1]]
offset_seg_trial1[, distance  := seg.z - original_intercept]
```

## Building models
```{r}
m.basic   <- lme(headingErr ~ 1, random = ~ 1|SubjectNo/Scene, data = offset_seg_trial1, method = "ML", na.action = na.exclude, control = list(opt="optim"))

m.dist.i  <- update(m.basic,     .~. + distance)
m.dist.s  <- update(m.dist.i,    random = ~ distance | SubjectNo/Scene)

m.scene.i <- update(m.dist.s,    .~. + Scene)
m.scene.s <- update(m.scene.i,   .~. + Scene:distance)
```

### Compare the models
```{r}
anova(m.basic, m.dist.i, m.dist.s, m.scene.i, m.scene.s)
```

### Show the full model
```{r}
summary(m.scene.s, corr = FALSE)
```

### *Post hoc* tests
#### Check the slopes
```{r}
contrast.matrix <- rbind(
  "Cloud"         = c(0, 1, 0, 0, 0, 0, 0, 0),
  "Line"          = c(0, 1, 0, 0, 0, 1, 0, 0),
  "Outline "      = c(0, 1, 0, 0, 0, 0, 1, 0),
  "Room "         = c(0, 1, 0, 0, 0, 0, 0, 1)
)
postHocs <-glht(m.scene.s, contrast.matrix) 
summary(postHocs, test = adjusted("none"))
summary(postHocs, test = adjusted("bonferroni"))
summary(postHocs, test = adjusted("fdr"))
```

#### Compare the slopes
```{r}
contrast.matrix <- rbind(
  "Line - Cloud"          = c(0, 0, 0, 0, 0, 1, 0, 0),
  "Outline - Cloud "      = c(0, 0, 0, 0, 0, 0, 1, 0),
  "Room - Cloud "         = c(0, 0, 0, 0, 0, 0, 0, 1),
  "Outline - line"        = c(0, 0, 0, 0, 0, -1, 1, 0),
  "Room - line"           = c(0, 0, 0, 0, 0, -1, 0, 1),
  "Room - Outline"        = c(0, 0, 0, 0, 0, 0, -1, 1) 
)
postHocs <-glht(m.scene.s, contrast.matrix)
summary(postHocs, test = adjusted("none"))
summary(postHocs, test = adjusted("bonferroni"))
summary(postHocs, test = adjusted("fdr"))
```




